A quantitative framework for investigating the reliability of empirical network construction

### 2019-01-15 manuscript/reply_to_reviewers.tex

		To make this clearer, we have rephrased this section and added a line (lines XX-XX) stating that we usually cannot determine the cause of all the zeros in an interaction matrix (we can identify obviously unfeasible interactions, but likely cannot say whether a zero for a rare species is because we did not observe enough individuals, there were not enough individuals to perform a particular interaction, or because the interaction is acutally unfeasible). We hope that this revision makes it clearer that the description of different sources of uncertainty is a conceptual guide only.

@@

	6. Process uncertainty poorly defined. [[done]]

		\begin{refquote}
		L76ff ‘Process uncertainty’ is not defined. The simplistic example of interaction uncertainty (fish eating a cactus) does not help the reader understand the detail of what is meant by ‘interaction uncertainty’. The two examples of ‘local constraints’ (weather and habitat) are operating on completely different temporal scales (note – it is defined differently in L109). I would regard the issue of weather as much closer to detection uncertainty (e.g. for a pollinator, it would be likely to be interacting if the weather was better), whereas the issue of habitat is closer to the authors’ ‘interaction uncertainty’ (the species don’t interact because they are not, or never, co-occurring in a habitat). Also if the species occur in different habitats then with an appropriate spatial scale of sampling then they do not co-occur – so the issue seems redundant. [[I suspect that the authors are thinking of a meta- or master network in much of their study, but this is not clear (or I have misunderstood and it needs to be explained better), i.e. the predicted presence of an interaction is not the presence of an interaction at the local site (taking detection and process uncertainty into account) but the ability to assess ‘interaction uncertainty’.]][[This is a bit separate from their issue]]
		\end{refquote}

		\textbf{R:} As our manuscript is not concerned with partitioning sources of uncertainty, we felt it was unproductive to get bogged down in a debate over the precise definitions of process vs. interaction uncertainty and which external influences might contribute to which sources (there is enough overlap that simple statements such as "bad weather increases process uncertainty" are, at best, incomplete). To remove this problem, we have rephrased the introduction and discussion to refer to the questions of whether two species \emph{can} interact under ideal conditions and whether they \emph{do} interact at a given site and time. We hope that this reframing, and the addition of clear statements that our framework is not intended to separate different sources of uncertainty, will remove the Reviewer's confusion.

		Our mention of habitat as a factor affecting the probability of species interacting at a site was not intended to refer to species using different habitats, but rather the possibility that habitat type might affect interaction probabilities. For example, a more open patch of forest might have different interaction probabilities than a denser patch even if the same set of species use both patches. The Reviewer is clearly correct that habitat also affects which species are present at a site. We include co-occurrence in process uncertainty since co-occurrence does not tell us much about whether an interaction is feasible under ideal conditions (which would certainly include co-occurrence). This speaks to our point above that external factors (habitat, weather, etc.) can affect multiple levels of uncertainty at once. In fact, habitat also likely affects detection uncertainty since it is often harder to observe interactions in dense vegetation. So, in short, separating sources of uncertainty based on the external factors which contribute to them is not a particularly useful endeavour.

@@

	7. Point about temporal scales of interaction [[done]]

		\begin{refquote}
		L76ff Different interactions occur at different temporal scales, so it is important to consider where the role of this study lies. For instance, a pollinator-flower interaction is quick (and even the evidence of it, e.g. pollen on the insect, is not long-lasting) whereas an active gall-former interaction could be present for a couple of months and could be detected for even longer (on senescing leaves).
		\end{refquote}

		\textbf{R:} Long-term interactions may be easier to detect, but this does not necessarily translate into reduced process uncertainty. Spatial variation in interaction probabilities will affect all interaction types, as does variation in abundances between years, so we cannot conceive of any interactions that are exempt from this issue. The timescale of an interaction (and the evidence it leaves) does affect detection uncertainty, so we have added a note in that section. Long-term interactions may fail to be detected, however, and we now add an example to make it clear that detection uncertainty applies to even long-term interactions such as gall-forming (indeed, our results suggest that uncertainty in gall-forming is quite high).

@@

		\textbf{R:} We have expanded our description of different types of priors and when researchers might prefer one over another. Following a comment from Reviewer 1 we have removed much of the mathematical background for the Bayesian approach, but this material is still present in the supplemental material. We hope that this simplifies the approach adequately.

	11. Integrate L155ff with previous section [[done]]

		\begin{refquote}
		L155ff I think it would be helpful for this section to be integrated with the previous section. It relies on the reader putting quite a lot of work in to understand the link between the two.
		\end{refquote}

		\textbf{R:} We have removed much of the introductory text explaining which quantity we are most interested in ($\lambda$) and now more explicitly state our goals at the end of the introduction. We hope that the transition to the methods is now less work for a reader.

@@

		\textbf{R:} We appreciate the Reviewer's desire for optimism, but we also selected a high-quality dataset specifically in order to demonstrate that empirically sampling all of the feasible interactions in a system is very unlikely. A lower-quality dataset would work just as well with our framework but would not highlight these difficulties so well. We have therefore kept this line as-is but have added another line (XX-XX) to show how the Bayesian framework provides a partial solution to the problems inherent in even high-quality empirical data.

		\begin{quotation}
		 The high spatiotemporal resolution of this dataset make it ideal for illustrating the difficulties in completely sampling a network; even with such an unusually high sampling effort, we anticipate that there will be many pairs of species which were rarely or never observed together. Using the Bayesian framework above, we can identify which potential interactions are more and less uncertain, allowing us to better predict the true structure of the metaweb.
		 \end{quotation}

	14. Line 283 seems to be a very important point and should be explained more clearly [[done]]

		\textbf{R:} Due to space constraints, we have refrained from adding an extensive description of Jensen's inequality here, but are confident that readers can find a fuller description in the online literature if they choose.

@@

	15. Line 291: does assuming probability of 1 for observed interactions introduce bias? [[done]]

		\begin{refquote}
		L291 I have wondered about this – does assuming a probability of 1 for observed interactions create a bias? The observed interactions are a stochastic set of the possible interactions, so by treating observed interactions as 1 and other (equally likely?) unobserved interactions as <1 will surely bias the network metrics. I’m not sure of the solution and would welcome thoughts on this in the paper.
		\end{refquote}

		\textbf{R:} As we are concerned with the metaweb (the set of feasible interactions) rather than the interactions which occurr at a given site on a given day, we do not think that assuming a probability of 1 for observed interactions introduces bias in our study. We have added a justification of setting the probability of observed interactions to 1 in \emph{Appendix S2}. Note that each posterior web is a prediction of the true metaweb and not a local realization of some interactions drawn from the feasible set. These local webs are more akin to our "filtered webs" in which observed interactions are not guaranteed to appear. We have also added a line (lines XX-XX) to make this clear.

		This is an interesting point, however, as systems with a large risk of false positives (e.g., pollination networks which assume all flower visitors provide pollination service) would be biased by assuming all observed interactions are truly feasible. Assuming that all interactions which are known to be feasible actually occur at each site would also introduce bias - I suspect that this is what the Reviewer may be thinking of. As described above, our study cannot isolate $\chi$ (the probability that a feasible interaction occurs at a particular site), so this is not a relevant question for the present work. Future studies with much, much more detailed data may be able to shed light on this.

@@

			\begin{quotation}
				Measures of network structure which are based on empirical networks that are missing interactions may differ substantially from the values that would be obtained if detection certainty and variation in interactions over space and time could be removed. To demonstrate this, we created a suite of filtered networks for each posterior network. Taking a posterior network as the "true" network, we randomly sampled 90\%, 80\%, 70\%, 60\%, 50\%, 40\%, 30\%, 20\%, and 10\% of the interactions to create a new "filtered" network.
			\end{quotation}

		Note that our model is not concerned with partitioning different sources of variation; the filtering levels we present therefore represent uncertainty from all sources. As such, comparing them directly to "typical sampling effort" would be an apples-to-oranges comparison. We do note that~\citet{Weinstein2017a} found a detectability of 23.3\% for interactions despite high sampling effort,~\citet{Jordano2016} found that about half of unobserved interactions did not qualify as "forbidden links", and~\citet{Bartomeus2013} found that 59\% of interactions were detected. We therefore do not think that the range of filtering levels we applied were particularly unreasonable (although we note that none of the above studies refer to plant-galler networks). That said, the Reviewer is correct that the values we chose were absolutely arbitrary. To make this clear, we now filter in 10\% increments from 90\% to 10\% to illustrate a broader range of uncertainty.

	17. Expand discussion of results on line 321 [[no space - had to remove network metrics.]]

@@

		\begin{refquote}
		L321 This is a really important and interesting set of results that are worthy of greater discussion. The issue of metrics from sampled networks is important, but gets lost in the paper. Please expand upon this.
		\end{refquote}

		\textbf{R:} Ultimately, length restrictions meant that we were obliged to remove our discussion of network metrics to an appendix. After adding the additional material requested by Reviewers in the methods, there simply was not space to discuss the network-level metrics in the main manuscript. We agree with the Reviewer that this is an extremely important question, but feel that it is essential to provide a clear and useable explanation of the basic Bayesian framework in the present manuscript. We hope to return to the question of how network metrics are impacted by sampling issues in more detail in future work.

### 2019-01-15 manuscript/reply_to_reviewers.tex

	\begin{refquote}
	Your manuscript has been assessed by four different referees who agree that you touch upon a very important problem. However, they all feel your manuscript needs substantial improvements. They provide excellent advise on how to revise your manuscript and you should carefully consider all their comments. Overall, you do not acknowledge important past contributions and do not clearly explain the importance of the methodological issues you cover in your study. Importantly, referee 1 feels the real novelty of your study is the consideration of the importance and complexity of choosing prior information in constructing networks. Obviously, this is an issue in the context of Bayesian approaches, which are not necessarily well understood by empiricists, precisely the audience your manuscript should address. Please, follow very closely the suggestions of the referees when revising your manuscript.

	\end{refquote}

	\textbf{R:} We appreciate the thoughtful feedback by the four referees. We take particular note of the comments regarding the structure and grounding of our introduction and have worked to address them.

	Reviewer 2 takes a different view of the purpose and scope of the manuscript from that of the other reviewers. We respect his/her ideas but feel that some are beyond the scope of the present manuscript. In particular, we do not feel that a full simulation study is necessary given the simplicity of our framework. We emphasise that we are not introducing a software package (although we do provide simple code to aid those who are new to the field), nor are we introducing an entirely new framework (as the other Reviewers point out, many components of our approach have been touched on by previous work). Thus, the novelty and impact of our work explicitly lies in connecting a Bayesian statistical approach to the problem of limited and uneven sampling of networks (driven by difference in species abundances, detectabilities, constrained time and budgets, etc.) and, we hope, in making this method more accessible to those without extensive statistical or modelling experience. Please note that Reviewer 3 identified this need explicitly. 
	% Tomas has a line break here, I'm not sure.
	Because of the difference between Reviewer 2 and the other Reviewers, we have opted to prioritise the majority view and focused first on comments by Reviewers 1, 3, and 4. However, we hope and trust that, in the course of these revisions, we have at least partially addressed Reviewer 2's concerns as well.

@@

% ----------------------------------------------------------------------
% ----------------------------------------------------------------------
{\Large \bf Reply to Reviewer \#1}
% ---------------------------------------

	The Reviewer complimented our manuscript as ``well-written'' and addressing the ``hugely important'' question prior choice in network analyses. He/she supports our suggestion that researchers use their system-specific knowledge when embarking upon Bayesian analyses, and has suggested that we restructure the manuscript (especially the introduction) in order to come more directly to the issue of prior choice. In the present revision we have taken this advice to heart and streamlined our introduction in order to expand our discussion of prior choice. In this revision, we have retained some of the introductory material which the Reviewer notes describes ``ground very well-trod'' in order to ensure that readers entirely new to Bayesian analysis will understand the problem at hand. We hope that the introduction now strikes a balance between providing essential background information for Bayesian novices and moving quickly enough for those who do not need such a gentle introduction. We thank the Reviewer for their feedback and address each point (prefaced by \textbf{R:}) below.

	1. Suggestion to refocus on prior selection

		\begin{refquote}
			In ecology more broadly, priors are treated with timidity, as if we couldn’t dare to leverage past work on our current understanding. Personally, I have always felt limited by this standard. I applaud the authors for taking on this challenge, and I would like to see an introduction that merits and debates this question in much more detail. ... Walking the reader through flat priors, informed priors and empirical priors is crucial for the importance of analysis to be understood by the reader. The use of empirical priors can be quite controversial, and should be at least touched on in the discussion. 
			\end{refquote}

@@

	2. Suggestion to add more literature

		\begin{refquote}
		The introduction flows well and is thoughtfully laid out. Given the enormous amount of literature in the field, it is not possible to provide a full set of citations. However, it seems remiss to not consider Jordano (2016) in the sampling section.
		\end{refquote}

		\textbf{R:} We thank the Reviewer for their compliments to our introduction and for the literature recommendations. We have incorporated these references as suggested (including Jordano, 2016 in the sampling section). Following comments from other reviewers, we have refined and restructured our introduction in the hope of more clearly establishing the goal of our manuscript. We hope that this revised introduction will also meet with the Reviewer's approval.

	3. Suggestion to de-emphasise MLE estimate and get straight to Bayes

@@

		\begin{refquote}
		It’s a bit confusing to lead the reader towards a Bayesian analysis, and then immediately start with the MLE estimate. Why is this needed at all? (L162-186). Just start at 187?
		\end{refquote}

		\textbf{R:} The MLE estimate is part of the Bayesian framework as it dictates the shape of the distribution that we use. We now introduce the MLE formally within this context (lines 229-231) and take care to be explicit when using it to explore the sample size needed in the absence of prior knowledge later (caption of Figure 3).

		Lines 229-231:

		\begin{quotation}
			The basis of a Bayesian approach to modelling the probability that an interaction occurs ($\lambda$) is combining the maximum likelihood estimate (MLE) of $\lambda$ with a prior distribution (described in the next section) and a normalising function. The MLE of $\lambda$ can be modelled as a Bernoulli trial based on the number of observed interactions $k$ and observed co-occurrences $n$: $\lambda = \frac{k}{n}$. The most appropriate prior distribution for a probability such as $\lambda$ is the beta distribution:
		\end{quotation}

@@

		Caption of figure 3:

		\begin{quotation}
			The number of observed co-occurrences needed to believe that an unobserved interaction cannot occur is very high (about 35; Fig. 3), and most datasets will not include this level of sampling for all pairs of species~\citep{Bartomeus2013}.
		\end{quotation}

	4. Suggestion to remove moments of the beta distribution

		\begin{refquote}
		I think a bit of space is wasted on defining the moments of the beta distribution. This is very googleable, and almost too thorough. I think the space is better utilised aligning the ecological challenge and the quantitative method.
		\end{refquote}

@@

		\textbf{R:} While we feel that a short introduction to the beta distribution is important to bring researchers new to Bayesian statistics up to speed (and give them some keywords to Google), we accept the Reviewer's suggestion to reduce the amount of space given to the beta. We have therefore moved the description of basic properties to Appendix S2. The remaining paragraph introducing the beta distribution now leads directly into the section describing prior selection.

	5. Novelty of the study not clear in current framing

		\begin{refquote}
		I’m wrestling with the novelty of the work as presented and whether it reaches the standard for publication at MEE. Certainly, much of this logic is laid out in other works. The authors are well aware of this and have made significant contributions to this topic in the last few years. In particular, the authors should try to be much more explicit about the contribution they hope to offer that hasn’t been covered. ...
		While it is true that none of the [suggested] papers do the exact same thing as this manuscript, they all	orbit the same topic. 
		\end{refquote}

		\textbf{R:} We thank the Reviewer for the literature suggestions and now include them in our introduction and/or discussion. We emphasise the board applicability of our approach across network types and systems with varying degrees of prior knowledge. We also emphasise that our approach is not restricted to species observed X times (as many predictive models are) and can include species not yet observed at a site (e.g., potential invaders). We hope that the contribution our manuscript makes is now clearer.

@@

	% 	Literature suggestions:
		% Jordano, P. (2016). Sampling networks of ecological interactions. Functional Ecology, 30(12), 1883–1893. doi:10.1111/1365-2435.12763
		% Bartomeus, I. (2013). Understanding Linkage Rules in Plant-Pollinator Networks by Using Hierarchical Models That Incorporate Pollinator Detectability and Plant Traits. PLoS ONE, 8(7), 1–9. doi:10.1371/journal.pone.0069200
		% Poisot, T., Cirtwill, A. R., Cazelles, K., Gravel, D., Fortin, M.-J., & Stouffer, D. B. (2016). The structure of probabilistic networks. Methods in Ecology and Evolution, 7(3), 303–312. doi:10.1111/2041-210X.12468
		% Poisot, T., Stouffer, D. B., & Gravel, D. (2015). Beyond species: why ecological interaction networks vary through space and time. Oikos, 124(3), 243–251. doi:10.1111/oik.01719
		% Graham, C. H., & Weinstein, B. G. (2018). Towards a predictive model of species interaction beta diversity. Ecology Letters. doi:10.1111/ele.13084
		% Gravel, D., Poisot, T., Albouy, C., Velez, L., & Mouillot, D. (2013). Inferring food web structure from predator-prey body size relationships. Methods in Ecology and Evolution, 4(11), 1083–1090. doi:10.1111/2041-210X.12103
		% Wells, K., & O’Hara, R. B. (2013). Species interactions: Estimating per-individual interaction strength and covariates before simplifying data into per-species ecological networks. Methods in Ecology and Evolution, 4(1), 1–8. doi:10.1111/j.2041-210x.2012.00249.x

\clearpage

% ----------------------------------------------------------------------
% ---------------------------------------------------------------------
{\Large \bf Reply to Reviewer \#2} 
% ---------------------------------------

	The Reviewer stated that our manuscript ``tackles a very interesting problem, quantifying the uncertainty of interactions" which he/she rates as ``one of the hottest topics in the field". He/she also points out that ``the introduction is particularly pleasant to read" and that we framed the problem well. The Reviewer also pointed out a number of weaknesses to the manuscript that we respond to one-by-one. In general, we feel that the Reviewer's comments reflect a high degree of statistical expertise; expertise that we do not expect to be shared by the bulk of our intended audience (empirical ecologists assembling new ecological networks). We have therefore prioritised comments by this and the other Reviewers that seemed most likely to improve the manuscript for readers who are relatively new to Bayesian analysis over concerns most relevant to a highly knowledgeable reader. We hope that our revised manuscript makes this target audience clearer, and that we have addressed the Reviewer's key concerns with our revision.

@@

	1. Lack of references [done]

		\begin{refquote}

			The fundamental question about predicting interactions given some uncertainty has been and is debated in many papers (see the seminal paper by Roger Guimer\`{a} and Marta Sales-Pardo, PNAS, 2009). Even if the proposed framework is probably not stated in its exact terms in the literature, bridges between existing approaches (beyond Ecology) and the one in the paper would be very welcomed. An appropriate discussion between points of convergence and difference would help the reader to appreciate the significance and the impact of the proposed methodology.

@@

		\begin{refquote}
			2/ network oversight: the approach considers that the interactions are independent, which is not the case in real data. Indeed, the paper is supposed to be “network-oriented“ but the methodology deals with independent interactions (e.g. the variables L,T,X and D introduced lines 62,77,101 are for instance not indexed by ij which could have suggested that the interactions were seen as a whole). Consequently, the mathematical framework remains quite simple and may not reflect nor model the processes governing the actual detection of interactions. Despite of this drawback, the proposed method is interesting but at least the authors should add some discussion on the limits of dealing with independent interactions,
		\end{refquote}

		\textbf{R:} We agree wholeheartedly that ecological interactions are often not independent. Indeed, some of the priors we discuss (e.g., those incorporating species' abundances or trait-matching) will introduce covariance between interactions. The Reviewer is correct that we did not initially mention this non-independence explicitly. Our aim is to keep our mathematical framework simple so that it is easy for those not familiar with Bayesian analysis to adopt. Nevertheless, non-independence of interactions is an important consideration. We are therefore happy to index all variables referring to interactions by ij and we have added an explicit statement (lines XX-XX) that some priors treat interactions independently while others will introduce covariance (e.g., by species).

		Lines XX-XX:

		\begin{quotation}
		    The shape parameters, or hyperparameters, may be set to particular values or derived from some data (see below). Note that the hyperparameters may be set to the same values for all interactions, allowed to vary independently for all interactions, or may incorporate non-independence between interactions (e.g., when the shape of the prior distribution depends upon species' abundances or traits).
		\end{quotation}

@@

	3. Question about identifiability of the model [done]

		\begin{refquote}

			the reader would appreciate that the authors discuss and prove the identifiability of the model. Indeed, the three levels of uncertainty are nested but one could wonder whether different parameters at the three levels can fit the same data with the same quality (i.e. no identifiability).  I would suggest this point to be addressed in a specific section.

@@

		Lines XX-XX:

		\begin{quotation}
			Note that these Bayesian models of $\lambda_{ij}$ are designed to quantify (and reduce) the total uncertainty about $\lambda_{ij}$. They do not address any of the nested sources of uncertainty in particular except through the choice of prior.
		\end{quotation}

	4. Request for a simulation study [done; thanks Tomas]

		\begin{refquote}
			the authors proposed an original approach based on a Bayesian framework. Beyond the identifiability question (see above), the reader can question the power of the method. Usually, a methodological proposal comes with a complete simulation study that is supposed to show  the proposed model is adapted/suitable to the question and efficient to solve it. In the paper in its present form, the authors assume that the reader will be convinced by the results obtained on a single real dataset… In my opinion, the reader can’t be fairly convinced: how powerful is the method? what can we say about the priors? how much data (n, k) is necessary to expect good results? An so on… Only a well-conducted simulation study can answer these questions.
		\end{refquote}

		\textbf{R:} We agree with the Reviewer that a full simulation study, based on recreating the sources of uncertainty in a data set generated from known processes, is an excellent way to demonstrate the power of a novel method. The novelty and impact of our work, however, is not in the method itself (several other Reviewers rightly point out that similar approaches have occasionally been used before) but in connecting a Bayesian statistical approach to the problem of limited and uneven sampling of networks and, we hope, in making this method more accessible to those without extensive statistical or modelling experience. In other words, what we try to achieve here is to alert empirical ecologists constructing and analysing networks to the uncertainties built into their work. We then try to provide them with simple tools for grasping the extent and consequences of typical patterns. Please note that other Reviewers (as expressed by Reviewer 3 in particular) find this a highly worthwhile objective.

@@

		What Reviewer 2 proposes would be more suitable for an entirely novel method and is substantially beyond the scope of the present study. There is indubitably a place for simulation studies in order to find the most powerful method once a variety of tools are in common use, especially for researchers aiming to convince modellers that their tool is more powerful. Our manuscript, however, is not aimed at those already comfortable with Bayesian approaches but rather at those who may be aware of the problems of uneven uncertainty but not aware of any way to include this information in their analyses. We are confident that even a very simple model which incorporates the differences in sampling across interactions (as ours does) is more powerful than a model which ignores this information completely, and we therefore do not intend to conduct a full-scale simulation study. We accept that this means that those already using more intricate Bayesian methods are unlikely to switch to our simpler version; it was never our intention that they should do so.

	5. Request for an extended results and discussion section [no actual response, just words]

		\begin{refquote}
			5/ results\&discussion too short: the reader is surprised to read 27 lines of raw results only… Given the amount of new methodology that is proposed, one can expect a complete description of its pros and cons. Obviously, a simulation study (see above) would enrich the results part. Forgetting about the length of these parts, it is still difficult to catch the key messages from the text, and it is not obvious to relate discussion and the obtained results (for instance,from l.343 to l.351).
		\end{refquote}

		\textbf{R:} We very much appreciate the Reviewer's point that the results and discussion do not clearly illustrate the point of the manuscript. Although we have not conducted a simulation study (see above), we have extensively revised these sections in order to highlight the main thread through the manuscript. Due to space limitations, we were unable to greatly expand either section (we prioritise the introduction and methods, which lay out the problem of uncertainty in networks and how it can be partially addressed), but we hope that the results now more clearly demonstrate how a Bayesian approach can address the uncertainty inherent in sampling.

@@

	6. Suggestions to improve notation [done? unless anyone else can figure out the last part...]

		\begin{refquote}
			6/ lack of rigorous notations: it is possible to understand the approach with the present notations but some improvements can help the reader because there are a series of inconsistencies. Here are some suggestions. The authors chose upper case letters L,T ,X,D for single entities whereas the mathematician is used to expect matrices or constants in upper case. Traditionally, given species i and j, we would consider interaction $L_ij$, feasibility $X_ij$, detection ability $D_ij$... \\
			Still, what is T?? not defined, never reused: is it a characteristics on i, on j, on both? \\
			How can be D<1 on l.169? D=0 or 1 since it says if an interaction is detectable or not... \\
			Moreover, L is reused later but is the number of interactions (l.100 supp.mat)… \\
			What is “N” in Figure 4? is it “n”? What is $n_ij$ and $k_ij$ l.266? Never defined, never reused. \\
			In the beginning of the paper, $\lambda$ is a probability (l.62) but it becomes a random variable (l.164): it would be more consistent to introduce before the notion of hyperparameters  (l.209-213) and to explain we consider that $\lambda$ is drawn into its distribution.
		\end{refquote}

@@

		Lines 373-379:

		\begin{quotation}
			To demonstrate how the use of data from a different system can affect the prior distribution and conclusions based on it, we repeated our analyses using priors derived from a much smaller Salix-galler-natural enemy system based around genotypes of a single Salix species (Barbour et al., 2016, Data available from the Dryad Digital Repository: https://doi.org/10.5061/dryad.g7805). This smaller system was much more densely-connected than that described in Kopelke et al. (2017) and provided unreasonable distributions for interaction probabilities (Appendix S6 ).
		\end{quotation}

	12. Why connectance and nestedness? [done?]

		\begin{refquote}
			-l.278: the authors investigate the consequence of uncertainty on network metrics. This question is of peculiar interest, but here it is restricted to the connectance and nestedness. Why these two metrics? Why not others? What is the impact of integrating uncertainty into the metrics computation? (we guess the answers but we could expect the authors develop these points).
		\end{refquote}

@@

		\begin{quotation}
			Nestedness was higher in the observed network (NODF=6.85) than in the posterior webs (6.31 $\leq NODF \leq$ 6.82; Fig. 5C), indicating that the posterior webs include many more interactions between specialists than the observed network. In addition, the stronger the detection filter, the farther apart were the nestedness of the observed and posterior webs. This suggests that the interactions included in the observed network are not a random subset of those included in the posterior webs.
		\end{quotation}

\clearpage

% ----------------------------------------------------------------------
% ----------------------------------------------------------------------
{\Large \bf Reply to Referee \#3}
% ---------------------------------------

	The Reviewer commented that our paper is, overall, very good and ``makes an important contribution" as ``a very nice attempt to show the broader community that the Bayesian approach is not so complex and has many advantages". We are glad that the Reviewer agrees about the importance of this message and appreciate his/her suggestions to improve the manuscript. We have taken care to add references and clarify the introduction, as well as to state explicitly that we are emphatically not suggesting that anyone sample with lower effort/intensity than they otherwise would. We considered the benefits of high-quality sampling to be so self-evident that it did not occur to us that our manuscript could be read as suggesting that extensive sampling is not worthwhile. We thank the Reviewer for pointing out the potential for confusion over this point and hope that it is now clear that Bayesian analyses are a complement to, not a replacement for, high-quality sampling. Below we address each of the Reviewer's suggestions in detail.

@@

	1. Add more references to the literature [[done]]
